Hybrid oddball - SSVEP BCI

### 2013-09-18 draftHybridPaper/draftHybridBCI.tex
more and more...

    \subsection{}
    \label{sec:4Discuss2}
    The second experiment showed that adding a visual oddball paradigm on top of a SSVEP stimulation did not affect significantly the power of the EEG response to the SSVEP stimulation in the concerned frequency.
    The SSVEP classification procedure described in \autoref{sec:2.3.3AnalysisExp3} relies on computing scores associated to different competing stimuli in order to attempt to identify the target stimulus.
    As our second experiment did not consider multiple competing stimuli (for each run, only one SSVEP stimulus at a specific frequency was shown on the screen), we did not attempt to classify the SSVEP responses.

    \subsection{}
    \label{sec:4Discuss3}
    The results from our 2~first experiments suggest the possibility of building a hybrid visual oddball-SSVEP BCI where both stimulations would physically overlap without compromising the detection of any of the 2~types of evoked response.
    Our third experiment confirmed those results showing the possibility of detecting both oddball ERPs and SSVEP activity simultaneously, and the results obtained suggest not only the feasibility of such hybrid BCI system but also a possible advantage of those systems over pure oddball and SSVEP ones in terms of communication rate.

%===================================================================================================================
%                                             5 CONCLUSION
%===================================================================================================================
\section{Conclusion}
\label{sec:6Conclusion}

>>>>

    \subsection{}
    \label{sec:4Discuss2}
%    The second experiment showed that adding a visual oddball paradigm on top of a SSVEP stimulation did not affect significantly the power of the EEG response to the SSVEP stimulation in the concerned frequency.
%    The SSVEP classification procedure described in \autoref{sec:2.3.3AnalysisExp3} relies on computing scores associated to different competing stimuli in order to attempt to identify the target stimulus.
%    As our second experiment did not consider multiple competing stimuli (for each run, only one SSVEP stimulus at a specific frequency was shown on the screen), we did not attempt to classify the SSVEP responses.
%    We can nevertheless simulate this competition for each level of the oddball condition (\emph{oddball v.s. no oddball}) with respect the 4~stimulation frequencies used in the experiment.
%    As the different frequencies were not actually competing, the observed accuracies should be higher than if the 4~stimuli were simultaneously shown on the screen; however we do not expect the effect of oddball stimulation to different

%===================================================================================================================
%                                             5 CONCLUSION
%===================================================================================================================
\section{Conclusion}
\label{sec:6Conclusion}
The results from our 2~first experiments suggest the possibility of building a hybrid visual oddball-SSVEP BCI where both stimulations would physically overlap without compromising the detection of any of the 2~types of evoked response.
Our third experiment confirmed those results showing the possibility of detecting both oddball ERPs and SSVEP activity simultaneously, and the results obtained suggest not only the feasibility of such hybrid BCI system but also a possible advantage of those systems over pure oddball and SSVEP ones in terms of communication rate.

All the results obtained in our study were obtained from offline analyses of the EEG data.
Therefore, further work should report on the feasibility of such hybrid oddball-SSVEP BCI in an online setting and focus on comparing the performance obtained with respect to the online performance of equivalent systems purely based on oddball ERP and SSVEP.
If successful, such systems would allow to increase the number of choices that an oddball-based BCI offers without decreasing the communication speed as well as overcome limitations in the number of stimuli that can be displayed on-screen for SSVEP-based BCIs.
%If successful, such system would allow to reduce the limitations of oddball-based BCIs where the communication speed increases with the number of target stimuli as well as the limitations in the number of stimuli that can be displayed on-screen for SSVEP-based BCIs.
